A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-22 main.tex
Describe the main example.

% Example of QCsp (mulmat)
{
\newcommand{\I}{\textrm{Int}}
\newcommand{\M}{\textrm{Mat}}
\begin{align*}
	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
\end{align*}
}

% mulmatの例

% Normal Conversion Rules

% \QCsp

>>>>

\newcommand{\I}{\textrm{Int}}
\newcommand{\M}{\textrm{Mat}}

$\text{mulmat}$ function in following code fragment generate a code for matrix multiplication.
$\text{mulmat}$ takes two integer which are the size of multiplicand matrix and generate a code.
The last integer to decide the size of multiplier matrix is given at runtime.
You can generate a code by applying two integers to $\text{mulmat}$.
We applied 3 and 5 in the second line and got $\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)$.
But this type is difficult to combine with other code because there are two $\%_\alpha$ for CSP.
\QPercent\ states that we can erase this $\%_\alpha$ under some conditions.

% Example of QCsp (mulmat)
{
\begin{align*}
	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
\end{align*}
}

% Describe "some conditions".
